SK5001 ANALISIS NUMERIK LANJUT

### 2021-10-25 Semester I/Analisis Numerik Lanjut/Catatan Kuliah.Rmd
new data

---
title: "SK5001 ANALISIS NUMERIK LANJUT"
subtitle: | 
    | Catatan Kuliah
    | Sebuah Usaha untuk Mencatat
author: | 
    | Ikang FADHLI
    | ikanx101.com
date: "`r format(Sys.time(), '%d %B %Y')`"
fontsize: 12pt
output: 
  pdf_document:
    number_sections: true
    toc: false
    fig_width: 7
    fig_height: 4
    fig_caption: true
    highlight: tango
header-includes:
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyfoot[CO,CE]{20921004@mahasiswa.itb.ac.id}
- \fancyfoot[LE,RO]{hal \thepage}

>>>>

---
title: "SK5001 ANALISIS NUMERIK LANJUT"
subtitle: | 
    | Catatan Kuliah
    | Menggunakan R
author: | 
    | Ikang FADHLI
    | ikanx101.com
date: "`r format(Sys.time(), '%d %B %Y')`"
fontsize: 12pt
output: 
  pdf_document:
    number_sections: true
    toc: false
    fig_width: 7
    fig_height: 4
    fig_caption: true
    highlight: tango
header-includes:
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyfoot[CO,CE]{20921004@mahasiswa.itb.ac.id}
- \fancyfoot[LE,RO]{hal \thepage}
